\Large \bf Polyglots : Crossing Origins by Crossing Formats

### 2013-05-08 main.tex
Fixed \ref{\todo{}}

\subsection{Attack vectors}

%In the scenario the attacker infiltrate the origin by uploading a polyglot. Infiltration could, however, be performed in more %than one way.
This paper identifies two vectors for infiltrating an origin, either via syntax 
injection, or content smuggling. In the case of syntax injection, existing content is manipulated
to become a polyglot, whereas with content smuggling, a polyglot is used to evade 
content filters.

@@

As explained in Section~\ref{\todo{ref}} there are two vectors for polyglot 
attacks; \emph{syntax injection} and \emph{content smuggling}. PDF is a suitable 
format for both vectors as it is both a text based format with error tolerant parsing, 
and has widespread acceptance as a document format, often preferred over 
other document formats.

@@

The behavior of cross-domain embedding of PDF resources is studied in the major 
browsers, i.e., Firefox, Safari, Opera, Google Chrome and Internet Explorer. 
The study shows that all major browsers are susceptible to the attacks outlined 
in Section~\ref{sec:vuln}, with some minor differences detailed below and summarized in Table~\ref{tab:comparison}.

>>>>

\subsection{Attack vectors}
\label{sec:vectors}
%In the scenario the attacker infiltrate the origin by uploading a polyglot. Infiltration could, however, be performed in more %than one way.
This paper identifies two vectors for infiltrating an origin, either via syntax 
injection, or content smuggling. In the case of syntax injection, existing content is manipulated
to become a polyglot, whereas with content smuggling, a polyglot is used to evade 
content filters.

@@

As explained in Section~\ref{sec:vectors} there are two vectors for polyglot 
attacks; \emph{syntax injection} and \emph{content smuggling}. PDF is a suitable 
format for both vectors as it is both a text based format with error tolerant parsing, 
and has widespread acceptance as a document format, often preferred over 
other document formats.

@@

The behavior of cross-domain embedding of PDF resources is studied in the major 
browsers, i.e., Firefox, Safari, Opera, Google Chrome and Internet Explorer. 
The study shows that all major browsers are susceptible to the attacks outlined 
in Section~\ref{sec:vuln}, with some minor differences detailed below and summarized in Table~\ref{tab:comparison}.
In Table~\ref{tab:comparison}, "Yes" for the columns "object" and "embed" indicates that the 
corresponding tag can be used to embed a PDF document, and for the column 
"Adobe is default" it indicates that Adobe Reader is the commonly default PDF reader.
